Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-10-14 draft.tex
add assumption that inside actors break ties in favor of status quo
Added 1 sentence and 2 footnotes regarding complexity of dependence on patron (for R3)

Player $c$ prefers reunification to recognized independence---a preference that is common to most states, and especially among those that fear the prospect of secessionist movements within their own borders. As discussed earlier, most states in the international system prefer any given secessionist conflict to be resolved by reunification. In practice we believe that in most cases there are many states that may act as player $c$ in our model, and often we observe groups of states like the OECD or the UN acting in this capacity.

@@

Analysis of the posited equilibrium proceeds most naturally by backward induction within each period. Thus we begin with the stage game between the government and secessionists.

@@

\subsection{If the Patron Withdraws Support}
Support by a foreign patron is, in almost all cases, necessary for the persistence of unrecognized statehood (Kolst\o \ 2006; Caspersen 2013). When there is no patron, or when the patron withdraws its support, military reconquest by the home state is likely. The only unrecognized state currently in existence which has been able to survive without a patron is Somaliland. Somaliland has been able to survive as long as it has because of the extreme weakness of the home state (Somalia).

>>>>

Player $c$ prefers reunification to recognized independence---a preference that is common to most states, and especially among those that fear the prospect of secessionist movements within their own borders. As discussed earlier, most states in the international system prefer any given secessionist conflict to be resolved by reunification. In practice we believe that in most cases there are many states that may act as player $c$ in our model, and often we observe groups of states like the OECD or the UN acting in this capacity. Modeling the international community as a single actor is a strong simplifying assumption, but by leaving the preferences of player $c$ quite general, the model can accommodate much of this diversity.\footnote{A variety of scholars, including Owtram (2011) and Coggins (2011) discuss the international relations of unrecognized states and variation across third-party states in their preferences with regard to unrecognized states.}

@@

Analysis of the posited equilibrium proceeds most naturally by backward induction within each period. Thus we begin with the stage game between the government and secessionists. We assume that the government and secessionists choose the Status Quo strategy whenever indifferent between it and any other strategy.

@@

\subsection{If the Patron Withdraws Support}
Support by a foreign patron is, in almost all cases, necessary for the persistence of unrecognized statehood (Kolst\o \ 2006; Caspersen 2013). When there is no patron, or when the patron withdraws its support, military reconquest by the home state is likely. The only unrecognized state currently in existence which has been able to survive without a patron is Somaliland. Somaliland has been able to survive as long as it has because of the extreme weakness of the home state (Somalia).\footnote{Owtram (2011) argues that, over time, unrecognized states can become sufficiently "consolidated" as to no longer be dependent on a patron for support. However, no cases other than Somaliland support this claim empirically.}
